What do incoming university students believe about open science practices in

### 2021-02-11 analysis/Manuscript.Rmd

```{r eligibility}

# all participants
n_all <- nrow(df)

# note re: eligibility
# only those who say "1" are eligible

age <- df %>%
  dplyr::count(age_lab)

el <- df %>%
  dplyr::count(eligibility_lab)

n <- el[5,2]
# filter(eligibility %in% 1)

>>>>

```{r inclusion}

# participant numbers (all & included cases)
df_all <- df
n_all <- nrow(df_all)
df <- df_all %>% 
  filter(exclude %in% "include") # only those who met the inclusion criterion
n <- nrow(df)

ex <- df_all %>% 
  filter(exclude %in% "exclude") %>% # n for those excluded
  nrow()

# note re: exclusion [all coded in `exclude` in preprocessing, 
# but need to summarise exclusion criteria here]
  # exclude those who are younger than 18
  # only those who say "1" to eligibility are included; all other responses are excluded
  # those whose `status` variable is an 'IP Address' are included

age <- df_all %>%
  dplyr::count(age_lab)

el <- df_all %>%
  dplyr::count(eligibility_lab)

status <- df_all %>% 
  dplyr::count(status_lab)
